Demo arXiv template

### 2023-02-09 paper/paper.tex
some build up on compute_indexes() example

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, borderline west={3pt}{0pt}{shadecolor}, breakable, sharp corners, enhanced, boxrule=0pt, frame hidden]}{\end{tcolorbox}}\fi

@@

Consider a commonly used drought index: Standardized
Precipitation-Evapotranspiration Index (SPEI) (Vicente-Serrano,
Beguería, and López-Moreno 2010). Its construction involves: 1)
calculating potential evapotranspiration (PET) from average temperature,
\texttt{tavg}, and its difference, \texttt{d}, with precipitation,
\texttt{prcp}, 2) aggregating difference series with a time scale, 3)
fitting the aggregated series with a chosen distribution to get density
values, and 4) converting the density values to normal quantiles. Under
the pipeline approach, SPEI will be constructed as:

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{DATA }\SpecialCharTok{\%\textgreater{}\%} 
  \FunctionTok{trans\_pet}\NormalTok{(}\AttributeTok{method =}\NormalTok{ thornthwaite, }\AttributeTok{var =}\NormalTok{ tavg) }\SpecialCharTok{\%\textgreater{}\%} 
  \FunctionTok{aggregate}\NormalTok{(}\AttributeTok{scale =} \DecValTok{12}\NormalTok{, }\AttributeTok{var =}\NormalTok{ d) }\SpecialCharTok{\%\textgreater{}\%} 
  \FunctionTok{normalise}\NormalTok{(}\AttributeTok{dist =}\NormalTok{ gamma, }\AttributeTok{fit\_method =}\NormalTok{ lmom) }\SpecialCharTok{\%\textgreater{}\%} 
  \FunctionTok{augment}\NormalTok{(}\AttributeTok{var =}\NormalTok{ .agg\_prcp)}
\end{Highlighting}
\end{Shaded}

\emph{Change the examples to two scales values, compare how indexes look
like}

Here each command corresponds to one step described above with
additional arguments specific to the step. The pipeline construction
produces the same index value as command like \texttt{spei(...)}, as
shown in Figure~\ref{fig-toy-example}, but with additional benefit:

\begin{itemize}
\tightlist
\item
  Multiple scales and multiple distributions can be fitted using the
  \texttt{c(...)} syntax to compare index values constructed from
  different parameterisations;
\item
  Intermediate results can be checked after each step; and
\item
  Additional steps and analysis can be wired into the workflow for index
  diagnostics and customised user need.
\end{itemize}

\emph{everyone is providing single command function, this is also the
same for spi}

\emph{may not worthwhile if only one index, as long as start changing}

\emph{just want to calculate index, single function is fine}

@@

{\centering \includegraphics[width=1\textwidth,height=0.3\textheight]{../figures/toy-example-spei.png}

@@

\caption{\label{fig-toy-example}Standardised Precipitation
Evapotranspiration Index (SPEI) calculated with two distribution fits in
Step 3 described above: generalised logistic (\texttt{glogist}) and
generalised extreme value (\texttt{gev}) distribution, using the
\texttt{wichita} data from the package \texttt{SPEI}.}

@@

@@

Data: 
# A tibble: 191 x 8
      id country                life_exp exp_sch avg_sch gni_pc   sch index
   <dbl> <chr>                     <dbl>   <dbl>   <dbl>  <dbl> <dbl> <dbl>
 1     1 Switzerland               0.984   0.917   0.924  0.983 0.920 0.962
 2     2 Norway                    0.973   1.01    0.867  0.978 0.939 0.963
 3     3 Iceland                   0.964   1.06    0.918  0.955 0.991 0.970
 4     4 Hong Kong, China (SAR)    1.01    0.960   0.815  0.973 0.887 0.954
 5     5 Australia                 0.993   1.17    0.848  0.936 1.01  0.979
 6     6 Denmark                   0.944   1.04    0.864  0.967 0.952 0.954
 7     7 Sweden                    0.969   1.08    0.841  0.952 0.960 0.960
 8     8 Ireland                   0.954   1.05    0.772  1.00  0.912 0.955
 9     9 Germany                   0.933   0.945   0.939  0.952 0.942 0.942
10    10 Netherlands               0.949   1.04    0.839  0.956 0.939 0.948
# ... with 181 more rows
\end{verbatim}

@@

Data: 
# A tibble: 191 x 13
      id country   life_~1 exp_sch avg_sch gni_pc   sch index0 index1 index2 index3 index4
   <dbl> <chr>       <dbl>   <dbl>   <dbl>  <dbl> <dbl>  <dbl>  <dbl>  <dbl>  <dbl>  <dbl>
 1     1 Switzerl~   0.984   0.917   0.924  0.983 0.920  0.962  0.963   1.67  0.978  0.933
 2     2 Norway      0.973   1.01    0.867  0.978 0.939  0.963  0.963   1.67  0.970  0.946
 3     3 Iceland     0.964   1.06    0.918  0.955 0.991  0.970  0.970   1.68  0.966  0.985
 4     4 Hong Kon~   1.01    0.960   0.815  0.973 0.887  0.954  0.956   1.65  0.992  0.908
 5     5 Australia   0.993   1.17    0.848  0.936 1.01   0.979  0.979   1.69  0.989  1.00 
 6     6 Denmark     0.944   1.04    0.864  0.967 0.952  0.954  0.954   1.65  0.947  0.953
 7     7 Sweden      0.969   1.08    0.841  0.952 0.960  0.960  0.960   1.66  0.966  0.960
 8     8 Ireland     0.954   1.05    0.772  1.00  0.912  0.955  0.956   1.66  0.955  0.925
 9     9 Germany     0.933   0.945   0.939  0.952 0.942  0.942  0.942   1.63  0.936  0.942
10    10 Netherla~   0.949   1.04    0.839  0.956 0.939  0.948  0.948   1.64  0.949  0.941
# ... with 181 more rows, 1 more variable: index5 <dbl>, and abbreviated variable name
#   1: life_exp
\end{verbatim}

@@

\caption{\label{fig-hdi-expr}Scatterplot matrix of country rankings
computed from different dimension reduction expressions in HDI:
geometric mean (\texttt{rank0}), arithmetic mean (\texttt{rank1}),
principal component analysis recommended weights (\texttt{rank2}), and
heavier weight on life expectancy, education, and GNI per capita
(\texttt{rank3} - \texttt{rank5}). Geometric mean, arithmetic mean, and
PCA produce similar rankings where countries are aligned in a diagnoal
line, while country rankings varies when compare among \texttt{rank3} to
\texttt{rank5}. Panel \texttt{rank5} vs.~\texttt{rank4} highlights a
cluster of countries that rank high by \texttt{rank5} but low by
\texttt{rank4}. The plot demonstrates the necessity to test on various
alternative expressions to verify the robustness of the method and to
capture distinctive characteristics of different countries.}

@@

\hypertarget{tbl-hdi-expr}{}
\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.2118}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1882}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1176}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1765}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.0824}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.0824}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.0706}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.0706}}@{}}
\caption{\label{tbl-hdi-expr}A selected number of countries with low
rankings when education is given a heavy weight (\texttt{index4}) while
ranks high when a heavier weight is given on GNI per capital
(\texttt{index5}).}\tabularnewline
\toprule()
\begin{minipage}[b]{\linewidth}\raggedright
country
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
life expectancy
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
education
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
GNI per capita
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
index3
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
index4
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
rank3
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
rank4
\end{minipage} \\
\midrule()
\endfirsthead
\toprule()
\begin{minipage}[b]{\linewidth}\raggedright
country
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
life expectancy
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
education
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
GNI per capita
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
index3
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
index4
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
rank3
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
rank4
\end{minipage} \\
\midrule()
\endhead
Andorra & 0.929 & 0.721 & 0.942 & 0.909 & 0.764 & 32 & 69 \\
Qatar & 0.912 & 0.684 & 1.023 & 0.900 & 0.741 & 34 & 83 \\
San Marino & 0.937 & 0.701 & 0.947 & 0.914 & 0.749 & 31 & 76 \\
Kuwait & 0.903 & 0.670 & 0.947 & 0.884 & 0.721 & 39 & 96 \\
Brunei Darussalam & 0.841 & 0.694 & 0.977 & 0.840 & 0.737 & 60 & 85 \\
\bottomrule()
\end{longtable}

\emph{what if the minimum value for GNI per capita is changed?}

The lower limit for GNI per capita is set to be the common log of \$100,
with justification provided in the technical notes as:

\begin{quote}
The low minimum value for gross national income (GNI) per capita, \$100,
is justified by the considerable amount of unmeasured subsistence and
nonmarket production in economies close to the minimum, which is not
captured in the official data
\end{quote}

The open source data provided by United Nations Development Programme
suggest the minimum GNI \emph{per capita} is \texttt{\$732} and this
opens the questions on how the index/ranking will change if the lower
minimum (\texttt{\$100}) is raised or decreased. We can answer this
question by testing on a set of different values using \texttt{.values}
in the function \texttt{swap\_values()}:

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{(res3 }\OtherTok{\textless{}{-}}\NormalTok{ res }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{swap\_values}\NormalTok{(}
    \AttributeTok{.module =}\NormalTok{ var\_trans, }\AttributeTok{.step =}\NormalTok{ rescale\_minmax, }\AttributeTok{.res =}\NormalTok{ gni\_pc,}
    \AttributeTok{.var =}\NormalTok{ min, }\AttributeTok{.values =} \FunctionTok{log10}\NormalTok{(}\DecValTok{700}\NormalTok{),}
    \AttributeTok{.raw\_data =}\NormalTok{ dt)) }
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
var_trans: `rescale_minmax(var = gni_pc, min = 2, max = 4.875061)` -> gni_pc0
\end{verbatim}

\begin{verbatim}
dim_red: `(life_exp * sch * gni_pc0)^(1/3)` -> index0
\end{verbatim}

\begin{verbatim}
var_trans: `rescale_minmax(var = gni_pc, min = 2.84509804001426, max = 4.875061)` ->
gni_pc1
\end{verbatim}

\begin{verbatim}
dim_red: `(life_exp * sch * gni_pc1)^(1/3)` -> index1
\end{verbatim}

Data: 
# A tibble: 191 x 10
      id country              life_~1 exp_sch avg_sch gni_pc gni_pc0 index0 gni_pc1 index1
   <dbl> <chr>                  <dbl>   <dbl>   <dbl>  <dbl>   <dbl>  <dbl>   <dbl>  <dbl>
 1     1 Switzerland            0.984   0.917   0.924   4.83   0.983  0.962   0.976  0.960
 2     2 Norway                 0.973   1.01    0.867   4.81   0.978  0.963   0.968  0.960
 3     3 Iceland                0.964   1.06    0.918   4.75   0.955  0.970   0.937  0.964
 4     4 Hong Kong, China (S~   1.01    0.960   0.815   4.80   0.973  0.954   0.961  0.951
 5     5 Australia              0.993   1.17    0.848   4.69   0.936  0.979   0.910  0.970
 6     6 Denmark                0.944   1.04    0.864   4.78   0.967  0.954   0.954  0.950
 7     7 Sweden                 0.969   1.08    0.841   4.74   0.952  0.960   0.932  0.953
 8     8 Ireland                0.954   1.05    0.772   4.88   1.00   0.955   1.00   0.956
 9     9 Germany                0.933   0.945   0.939   4.74   0.952  0.942   0.932  0.936
10    10 Netherlands            0.949   1.04    0.839   4.75   0.956  0.948   0.937  0.942
# ... with 181 more rows, and abbreviated variable name 1: life_exp
\end{verbatim}

The function computes the GNI \emph{per capita} in both the original
value (\texttt{gni\_pc0}) and the new value provided
(\texttt{gni\_pc1}). All the subsequent operations are also computed for
both cases and result in \texttt{index0} and \texttt{index1}.

{\centering \includegraphics{paper_files/figure-pdf/unnamed-chunk-8-1.pdf}

>>>>

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, sharp corners, breakable, boxrule=0pt, borderline west={3pt}{0pt}{shadecolor}, frame hidden, interior hidden]}{\end{tcolorbox}}\fi

@@

Consider a commonly used drought index: Standardized
Precipitation-Evapotranspiration Index (SPEI) (Vicente-Serrano,
Beguería, and López-Moreno 2010). Its construction involves:

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  transform the average temperature (\texttt{TMED}) into potential
  evapotranspiration (\texttt{pet})
\item
  combine precipitation (\texttt{prcp}) and potential evapotranspiration
  (\texttt{pet}) into a single variable \texttt{diff}
\item
  aggregate the difference series with a sliding window
  (\texttt{.scale})
\item
  fit a distribution to the aggregated series, and
\item
  derive the index value from the normal density values.
\end{enumerate}

Conventionally approach may combine all these steps into a single
function, with some level of modularity. However, these modules may only
work for the selected index offered by the package.

Under the pipeline approach, analysts first need to identify which
module each step belongs to.

Below shows the pseudocode for constructing SPEI with the pipeline:

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{DATA }\SpecialCharTok{\%\textgreater{}\%} 
  \FunctionTok{var\_trans}\NormalTok{(}\AttributeTok{.method =}\NormalTok{ thornthwaite, }\AttributeTok{Tave =}\NormalTok{ TMED, ..., }\AttributeTok{.new\_name =} \StringTok{"pet"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{dim\_red}\NormalTok{(}\AttributeTok{diff =}\NormalTok{ prcp }\SpecialCharTok{{-}}\NormalTok{ pet) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{aggregate}\NormalTok{(}\AttributeTok{.var =}\NormalTok{ diff, }\AttributeTok{.scale =} \DecValTok{12}\NormalTok{, }\AttributeTok{.new\_name =} \StringTok{"agg"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{dist\_fit}\NormalTok{(}\AttributeTok{.method =} \StringTok{"lmoms"}\NormalTok{, }\AttributeTok{.var =}\NormalTok{ agg, }\AttributeTok{.dist =}\NormalTok{ DIST) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{augment}\NormalTok{(}\AttributeTok{.var =}\NormalTok{ agg)}
\end{Highlighting}
\end{Shaded}

The pipeline construct allows for multiple \texttt{.scales} and
\texttt{.dist} to be evaluated in \texttt{aggregate()} and
\texttt{dist\_fit()} to compare index under different parameterisations.
The result can then be passed into the \texttt{ggplot2} to crease
visualisation. Figure~\ref{fig-toy-example} compares the SPEI calculated
with two distributions (log-logistic and pearson III).

Apart from evaluating multiples parameters, the pipeline approach allows
the the steps written for one index can be directly extrapolate to
another index building within the pipeline. The flexibility of the
pipeline also integrate well with other existing packages, for examples,
fitting distributions using L-moment is commonly used when constructing
drought indexes. The package \texttt{lmomco} provides general L-moment
fits to a wide range of distributions and users can easily access to all
the distributions within the pipeline.

@@

{\centering \includegraphics{paper_files/figure-pdf/fig-toy-example-1.pdf}

@@

\caption{\label{fig-toy-example}Standardised Precipitation
Evapotranspiration Index (SPEI) calculated with two distribution fits in
Step 3 described above: generalised logistic and pearson III
distribution, using the \texttt{wichita} data from the package
\texttt{SPEI}.}

@@

Drought, as a complex natural hazard event, is difficult to measure.

There is no uniform definition on drought (\textbf{ref?}), a range of
drought indexes are usually used simultaneously to quantify the severity
of a drought event.

In the package PACKAGE, a collection of drought indexes have been
implemented, including the most commonly used SPI and SPEI
(\texttt{idx\_spi()} and \texttt{idx\_spei()}). They can be computed
collectively on a dataset under \texttt{compute\_indexes()}:

The individual index functions are convenient wrappers around the
pipeline building blocks.

For SPI and SPEI, the wrapper functions also allow for multiple inputs
of scales and distribution parameters (\texttt{.scale} and
\texttt{.dist}) to allow computation on multiple time scale and
distribution fitting. The following code compute the two indexes (SPI
and SPEI) for different time scales (6, 12, 18, 24, 30, 36) and
different distributions (Pearson III, log-logistic, lognormal, and
general extreme value distributions) for {[}NUMBER{]} weather stations
in Eastern Australia shown in Figure~\ref{fig-station-map}: (TODO:
should talk about the data source)

{\centering \includegraphics{paper_files/figure-pdf/fig-station-map-1.pdf}

\caption{\label{fig-station-map}\ldots{}}

@@

Data: 
# A tibble: 191 x 8
      id country                life_exp exp_sch avg_sch gni_pc   sch index
   <dbl> <chr>                     <dbl>   <dbl>   <dbl>  <dbl> <dbl> <dbl>
 1     1 Switzerland               0.984   0.917   0.924  0.983 0.920 0.962
 2     2 Norway                    0.973   1       0.867  0.978 0.933 0.961
 3     3 Iceland                   0.964   1       0.918  0.955 0.959 0.959
 4     4 Hong Kong, China (SAR)    1       0.960   0.815  0.973 0.887 0.952
 5     5 Australia                 0.993   1       0.848  0.936 0.924 0.951
 6     6 Denmark                   0.944   1       0.864  0.967 0.932 0.948
 7     7 Sweden                    0.969   1       0.841  0.952 0.920 0.947
 8     8 Ireland                   0.954   1       0.772  1     0.886 0.945
 9     9 Germany                   0.933   0.945   0.939  0.952 0.942 0.942
10    10 Netherlands               0.949   1       0.839  0.956 0.919 0.941
# ... with 181 more rows
\end{verbatim}

@@

Data: 
# A tibble: 191 x 13
      id country   life_~1 exp_sch avg_sch gni_pc   sch index0 index1 index2 index3 index4
   <dbl> <chr>       <dbl>   <dbl>   <dbl>  <dbl> <dbl>  <dbl>  <dbl>  <dbl>  <dbl>  <dbl>
 1     1 Switzerl~   0.984   0.917   0.924  0.983 0.920  0.962  0.963   1.67  0.978  0.933
 2     2 Norway      0.973   1       0.867  0.978 0.933  0.961  0.961   1.66  0.969  0.942
 3     3 Iceland     0.964   1       0.918  0.955 0.959  0.959  0.959   1.66  0.963  0.959
 4     4 Hong Kon~   1       0.960   0.815  0.973 0.887  0.952  0.953   1.65  0.986  0.907
 5     5 Australia   0.993   1       0.848  0.936 0.924  0.951  0.951   1.65  0.980  0.932
 6     6 Denmark     0.944   1       0.864  0.967 0.932  0.948  0.948   1.64  0.945  0.937
 7     7 Sweden      0.969   1       0.841  0.952 0.920  0.947  0.947   1.64  0.962  0.928
 8     8 Ireland     0.954   1       0.772  1     0.886  0.945  0.947   1.64  0.952  0.904
 9     9 Germany     0.933   0.945   0.939  0.952 0.942  0.942  0.942   1.63  0.936  0.942
10    10 Netherla~   0.949   1       0.839  0.956 0.919  0.941  0.941   1.63  0.947  0.926
# ... with 181 more rows, 1 more variable: index5 <dbl>, and abbreviated variable name
#   1: life_exp
\end{verbatim}

@@

\caption{\label{fig-hdi-expr}Comparing country ranks from six different
index constructions: geometric mean (\texttt{rank0}), arithmetic mean
(\texttt{rank1}), principal component analysis recommended weights
(\texttt{rank2}), and heavier weight on life expectancy, education, and
GNI per capita (\texttt{rank3} - \texttt{rank5}). Geometric mean,
arithmetic mean, and PCA produce similar rankings where countries are
aligned in a diagnoal line, while country rankings varies when compare
among \texttt{rank3} to \texttt{rank5}. Panel \texttt{rank5}
vs.~\texttt{rank4} highlights a cluster of countries that rank high by
\texttt{rank5} but low by \texttt{rank4}. The plot demonstrates the
necessity to test on various alternative expressions to verify the
robustness of the method and to capture distinctive characteristics of
different countries.}

@@

\hypertarget{tbl-hdi-expr}{}
\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.2118}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1882}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1176}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.1765}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.0824}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.0824}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.0706}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 14\tabcolsep) * \real{0.0706}}@{}}
\caption{\label{tbl-hdi-expr}A selected number of countries with low
rankings when education is given a heavy weight (\texttt{index4}) while
ranks high when a heavier weight is given on GNI per capital
(\texttt{index5}).}\tabularnewline
\toprule()
\begin{minipage}[b]{\linewidth}\raggedright
country
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
life expectancy
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
education
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
GNI per capita
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
index3
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
index4
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
rank3
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
rank4
\end{minipage} \\
\midrule()
\endfirsthead
\toprule()
\begin{minipage}[b]{\linewidth}\raggedright
country
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
life expectancy
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
education
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
GNI per capita
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
index3
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
index4
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
rank3
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
rank4
\end{minipage} \\
\midrule()
\endhead
Andorra & 0.929 & 0.721 & 0.942 & 0.909 & 0.764 & 32 & 69 \\
Qatar & 0.912 & 0.684 & 1.000 & 0.898 & 0.739 & 34 & 84 \\
San Marino & 0.937 & 0.701 & 0.947 & 0.914 & 0.749 & 30 & 76 \\
Kuwait & 0.903 & 0.670 & 0.947 & 0.884 & 0.721 & 39 & 96 \\
Brunei Darussalam & 0.841 & 0.694 & 0.977 & 0.840 & 0.737 & 60 & 85 \\
\bottomrule()
\end{longtable}
